---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# devrcap
[![Travis build status](https://travis-ci.org/CorradoLanera/devrcap.svg?branch=master)](https://travis-ci.org/CorradoLanera/devrcap)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/CorradoLanera/devrcap?branch=master&svg=true)](https://ci.appveyor.com/project/CorradoLanera/devrcap)
[![Coverage status](https://codecov.io/gh/CorradoLanera/devrcap/branch/master/graph/badge.svg)](https://codecov.io/github/CorradoLanera/devrcap?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/devrcap)](https://cran.r-project.org/package=devrcap)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

The goal of devrcap is to collect code and data for the capstone assignments of the Coursera specialization "Mastering Software Development in R."

You can install the development version from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CorradoLanera/devrcap")
```

## Code of Conduct
Please note that the 'devrcap' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
